Spin canonical rings of log stacky curves

### 2015-07-10 surfaces-write-up/surface-write-up.tex
changed lemma on P1xP1 to include hirzabrook surfaces and give explicit degrees

\noindent
has a minimal presentation consisting of the $\sum_{i = 0}^{r}
{{m + i} \choose {i}}$ generators $\frac{u^{d_i} x^{\vec{v}}}{x_k^{c_i}}$
where $\vec{v} \in \bz_{\geq 0}^{m + 1}$ such that $\sum_{j = 0}^{m}
v_j = c_i$ and $z$ \todo{how many?} relations of the form

\[
	x^{\vec{u}} x^{\vec{v}} = x^{\vec{w}} x^{\vec{z}}
\]

@@

\begin{proof}
We know $u$ is a minimal generator in degree $1$. If $x^{\vec{v}}$
were not minimal for $\deg \vec{v} = c_i > 0$ for some $i > 0$, then
\end{proof}

@@

\section{Canonical Rings on \texorpdfstring{$\bp^1 \times \bp^1$}{}}
\begin{lem}
If $D=\sum_{i=1}^m \alpha_i C_i$ for some curve $C_i\in \mathbb{P}^1\times \mathbb{P}^1$, such that $C_1, \ldots, C_4$ are independent hyperplanes.  Then each $C_i$ corresponds to a bi-homogeneous polynomial $f_i$ where $f_1$ and $f_2$ are independent linear polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent linear polynomials in $y_0$ and $y_1$.  Then $D$ is generated in degree at most \todo{add} with relations in degree at most \todo{add}.
\end{lem}
\begin{proof}
Let $(d_i, d_i')$ be the bi-degrees of $f_i$.

@@

For $i \in \{1, \ldots, m\}$ satisfying 
\begin{equation}\label{eqn:condition-for-e_i}
	d_i \sum_{k=1}^m d_k' \alpha_k = d_i' \sum_{k=1}^m d_k \alpha_k,
\end{equation}
define
\[
	\epsilon_i := (\prod_{k \ne i} f_k^{-\alpha \ell_i \gcd(d_i, d_i')}) (f_i^{\ell_i \frac{\gcd(d_i, d_i')}{d_i + d_i'}\sum_{k \ne i} \alpha_k (d_k + d_k')}) \in H^0(\ell_i \gcd(d_i, d_i') D).
\]
\todo{Peter: This equation above is very asymmetric in $d_i$ and $d_i'$.  Can we replace this with something in degree $\gcd(d_i, d_i')$? Otherwise, maybe its wrong and no such element actually exists in that degree (I think it exists, but will check again later to be sure)?}
For $i, j \in \{1, \ldots, m\}$ satisfying
\begin{equation}\label{eqn:condition-e_i,j-i}
	d_i \sum_{k=1}^m \alpha_k d_k' > d_i' \sum_{k=1}^m \alpha_k d_k
\end{equation}
and
\begin{equation}\label{eqn:condition-e_i,j-j}
	d_j \sum_{k=1}^m \alpha_k d_k' < d_j' \sum_{k=1}^m \alpha_k d_k
\end{equation}
then define
\[
	\epsilon_{i, j} = (\prod_{k = 1}^m f_k^{-\alpha \ell_{i,j} (d_i d_j' - d_j d_i')}) {f_i}^{s_1} {f_j}^{s_2} \in H^0(\ell_{i,j}(d_i d_j' - d_j d_i')D)
\]
where
\[
	s_1 = d_j' \sum_{k \ne i,j} \alpha_k d_k - d_j \sum_{k\ne i, j} \alpha_k d_k'
\]
and
\[
	s_2 = d_i' \sum_{k \ne i,j} \alpha_k d_k - d_i \sum_{k \ne i, j} \alpha_k d_k'.
\]
Let $E$ be the set of $\epsilon_i$ and $\epsilon_{i,j}$ given above, satisfying the respective conditions.
$E$ satisfies the conditions of proposition \todo{cite earlier proposition}, so by applying that proposition $R_D$ is generated in degree at most \todo{insert number}.
\end{proof}

>>>>

\noindent
has a minimal presentation consisting of the $\sum_{i = 0}^{r}
{{m + i} \choose {i}}$ generators $\frac{u^d x_{\vec{v}}}{x_k^{c_i}}$
where $\vec{v} \in \bz_{\geq 0}^{m + 1}$ such that $\sum_{j = 0}^{m}
v_j = c_i$ and $z$ relations of the form
\[
	x_{\vec{u}} x_{\vec{v}} = x_{\vec{w}} x_{\vec{z}}
\]

\noindent
when $\sum_{i = 0}^{m + 1} u_i + v_i = \sum_{i = 0}^{m + 1} w_i + z_i$
\todo{fix this condition to make it right}
or of the form

\[
	x_{\vec{u}} x_{\vec{v}} = x_{\vec{w}} x_{\vec{z}}
\]

@@

\begin{proof}

\end{proof}

@@

\section{Canonical Rings on \texorpdfstring{$F_k$}{}}
\begin{defn}
Suppose $D = \sum_{i=1}^m \alpha_i C_i \in \mathbb{Q} \otimes \di(F_k)$.  Then define 
\begin{equation}\label{eqn:define-T=(D)}
	T_=(D) = \left\{i \in \{1, \ldots, m\}: d_i \sum_{k=1}^m d_k' \alpha_k = d_i' \sum_{k=1}^m d_k \alpha_k \right\},
\end{equation}
\begin{equation}\label{eqn:define-T+(D)}
	T_+(D) = \left\{ i \in \{1, \ldots, m\}:  \vphantom{\sum_{k=1}^m} d_i \sum_{k=1}^m \alpha_k d_k' > d_i' \sum_{k=1}^m \alpha_k d_k \right\},
\end{equation}
and
\begin{equation}\label{eqn:define-T-(D)}
	T_-(D) = \left\{ j \in \{1, \ldots, m\}: d_j \sum_{k=1}^m \alpha_k d_k' < d_j' \sum_{k=1}^m \alpha_k d_k s \right\}.
\end{equation}
\end{defn}

\begin{lem}
If $D=\sum_{i=1}^m \alpha_i C_i$ for some curve $C_i\in F_k$, such that $C_1, \ldots, C_4$ are independent curves with bi-degrees (1,0), (1,0), (0,1), and (0,1) respectively.  Then each $C_i$ corresponds to a polynomial $f_i$ where $f_1$ and $f_2$ are independent linear polynomials in $x_0$ and $x_1$ and $f_3$ and $f_4$ are independent linear polynomials in $y_0$ and $y_1$.  Then $D$ is generated in degree at most
\[
	\sum_{i\in T_=(D)} \gcd(d_i, d_i')\ell_i + \sum_{i\in T_+(D) \atop j\in T_-(D)} (d_i d_j'- d_j d_i')\ell_{i,j}
\]
 with relations in degree at most \todo{add}.
\end{lem}
\begin{proof}
Let $(d_i, d_i')$ be the bi-degrees of $f_i$.

@@

For $i \in T_=(D)$
define
\[
	\epsilon_i := (\prod_{k \ne i} f_k^{-\alpha \ell_i \gcd(d_i, d_i')}) (f_i^{\ell_i \frac{\gcd(d_i, d_i')}{d_i + d_i'}\sum_{k \ne i} \alpha_k (d_k + d_k')}) \in H^0(\ell_i \gcd(d_i, d_i') D).
\]
For $i \in T_+(D)$ and $j \in T_-(D)$, define
\[
	\epsilon_{i, j} = (\prod_{k = 1}^m f_k^{-\alpha \ell_{i,j} (d_i d_j' - d_j d_i')}) {f_i}^{s_1} {f_j}^{s_2} \in H^0(\ell_{i,j}(d_i d_j' - d_j d_i')D)
\]
where
\[
	s_1 = d_j' \sum_{k \ne i,j} \alpha_k d_k - d_j \sum_{k\ne i, j} \alpha_k d_k'
\]
and
\[
	s_2 = d_i' \sum_{k \ne i,j} \alpha_k d_k - d_i \sum_{k \ne i, j} \alpha_k d_k'.
\]
Let $E$ be the set of $\epsilon_i$ and $\epsilon_{i,j}$ given above, satisfying the respective conditions.
$E$ satisfies the conditions of proposition \todo{cite earlier proposition}, so by applying that proposition $R_D$ is generated in degree at most
\[
	\sum_{i\in T_=(D)} \gcd(d_i, d_i')\ell_i + \sum_{i\in T_+(D) \atop j\in T_-(D)} (d_i d_j'- d_j d_i')\ell_{i,j}.
\]

\end{proof}
